DRAFT

### 2022-11-02 Draft.Rmd
Update Draft.Rmd

# Distance
df2 <- separate(df2, center1distance, ' ', into =
                  c('distance', 'miles'))
df2 <- select(df2, -miles)
df2$distance <- as.numeric(df2$distance)
```
* The original *accommodationtype* variable was tranformed into new *accomtype* factor variable.
```{r}
df2 <- separate(df2, accommodationtype, '@', into = 
                 c('word', 'acctype'))
df2 <- select(df2, -word)
df2 <- mutate(df2, acctype_f = factor(acctype))
```
* *trueprice* variable was generated by dividing the original *price* variable by *price_night*
```{r}
df2 <- separate(df2, price_night, ' ', into =
                     c('pr','word', 'nights', 'night'))
df2 <- select(df2, -pr)
df2 <- select(df2, -night)
df2 <- select(df2, -word)
df2$nights <- as.numeric(df2$nights)
df2$trueprice <- df2$price/df2$nights
```
* *season* variable was created based on the *month* variable
```{r}
df2 <- df2 %>%
  mutate(season = case_when(month == 12 | month == 1 |month == 2 ~ 'winter',
                            month == 3 | month == 4 |month == 5 ~ 'spring',
                            month == 6 | month == 7 |month == 8 ~ 'summer',
                            month == 9 | month == 10 |month == 11 ~ 'autumn'))
```
* With the help of the existing *starrating* variable new *class* variable was generated
```{r}
df2 <- df2 %>%
  mutate(class = case_when(starrating == 1.0 | starrating == 1.5 ~ 'tourist',
                           starrating == 2.0 | starrating == 2.5 ~ 'standard',
                           starrating == 3.0 | starrating == 3.5 ~ 'comfort',
                           starrating == 4.0 | starrating == 4.5 ~ 'first class',
                           starrating == 5.0 ~ 'luxury'))
```

@@

### *Factor variables*

@@

### • Country
```{r echo=FALSE}
kable(count(df2, addresscountryname) %>% arrange(desc(n)))
```

@@

### *Binary variables*

@@

## 1.3 Findings
### • Mean prices for countries
```{r echo=FALSE}
datasummary(trueprice*addresscountryname ~ Mean + Max + Min, data=df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
```

### • Plot for diff years diff countries
```{r}
df3 <- aggregate(trueprice ~ addresscountryname + year, 
                 data=df2, 
                 function(x) { 
                   c(mean_price = mean(x)) 
                 })
ggplot(data = df3, aes(x=year, y=trueprice, fill=addresscountryname)) + 
  geom_bar(stat='identity') + facet_wrap(~addresscountryname) +
  geom_text(aes(label = round(trueprice)), vjust = -0.2)
```

>>>>

# Distance
df2 <- separate(df2, center1distance, ' ', into =
                  c('distance', 'miles'))
df2 <- select(df2, -miles)
df2$distance <- as.numeric(df2$distance)

df2$country <- as.factor(df2$addresscountryname)
df2 <- select(df2, -addresscountryname)
```
* The original *accommodationtype* variable was tranformed into new *acctype_f* factor variable.
```{r}
df2 <- separate(df2, accommodationtype, '@', into = 
                 c('word', 'acctype'))
df2 <- select(df2, -word)
df2 <- mutate(df2, acctype_f = factor(acctype))
```
* *trueprice* variable was generated by dividing the original *price* variable by *price_night*
```{r}
df2 <- separate(df2, price_night, ' ', into =
                     c('pr','word', 'nights', 'night'))
df2 <- select(df2, -pr)
df2 <- select(df2, -night)
df2 <- select(df2, -word)
df2$nights <- as.numeric(df2$nights)
df2$trueprice <- df2$price/df2$nights
```
* *season* variable was created based on the *month* variable
```{r}
df2 <- df2 %>%
  mutate(season = case_when(month == 12 | month == 1 |month == 2 ~ 'winter',
                            month == 3 | month == 4 |month == 5 ~ 'spring',
                            month == 6 | month == 7 |month == 8 ~ 'summer',
                            month == 9 | month == 10 |month == 11 ~ 'autumn'))
df2$season <- as.factor(df2$season)
```
* With the help of the existing *starrating* variable new *class* variable was generated
```{r}
df2 <- df2 %>%
  mutate(class = case_when(starrating == 1.0 | starrating == 1.5 ~ 'tourist',
                           starrating == 2.0 | starrating == 2.5 ~ 'standard',
                           starrating == 3.0 | starrating == 3.5 ~ 'comfort',
                           starrating == 4.0 | starrating == 4.5 ~ 'first class',
                           starrating == 5.0 ~ 'luxury'))
df2$class <- as.factor(df2$class)
```

@@

## *Factor variables*

@@

### • Country
```{r echo=FALSE}
kable(count(df2, country) %>% arrange(desc(n)))
```

@@

## *Binary variables*

@@

## 1.3 Findings
### • Mean prices for countries
```{r echo=FALSE}
datasummary(trueprice*country ~ Mean + Max + Min, data=df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
```

### • Plot for diff years diff countries
```{r}
df3 <- aggregate(trueprice ~ country + year, 
                 data=df2, 
                 function(x) { 
                   c(mean_price = mean(x)) 
                 })
ggplot(data = df3, aes(x=year, y=trueprice, fill=country)) + 
  geom_bar(stat='identity') + facet_wrap(~country) +
  geom_text(aes(label = round(trueprice)), vjust = -0.2)
```
